Response to the defense feedback

### 2021-06-19 Chapter-3/Chapter-3.tex
Updates from Overleaf

Even for the up-to-date version of OpenSSL, \detect{} still find several
side-channel leakages. Figure~\ref{chapter3:fig:unknown_leakage} shows an unknown leakage site in OpenSSL 1.1.1. It is a secret-dependent control flow transfers. 
However, as the branch is inside a loop and a bit shift function causes the branch leak different bits from the sensitive buffer. The function can leak the last digit from big number \textbf{X}. The leakage is severe due to the 
function \textsf{BN\_rshift1}. Each time, function \textsf{BN\_rshift1}
shifts \textbf{X} right by one and places the result in \textbf{X}. Therefore,
an attacker can infer multiple bits of \textbf{X} by observing the branch at line 3.

>>>>

Even for the up-to-date version of OpenSSL, \detect{} still find several
side-channel leakages. Figure~\ref{chapter3:fig:unknown_leakage} shows an unknown leakage site in OpenSSL 1.1.1. It is a secret-dependent control flow transfers. 
However, as the branch is inside a loop and a bit shift function causes the branch leak different bits from the sensitive buffer. The function can leak the last digit from big number \textbf{X}. The leakage is severe due to the 
function \textsf{BN\_rshift1}. Each time, function \textsf{BN\_rshift1}
shifts \textsf{X} right by one and places the result in \textsf{X}. Therefore,
an attacker can infer multiple bits of \textsf{X} by observing the branch at line 3.
